Acceleration of plague outbreaks in the second pandemic

### 2020-07-12 ms_text.tex
author contributions

% Please include corresponding author, author contribution and author declaration information
\authorcontributions{{\color{red}Please provide details of author contributions here.}}
%%\authordeclaration{{\color{red}Please declare any conflict of interest here.}}
%%\equalauthors{\textsuperscript{1}A.O.(Author One) and A.T. (Author Two) contributed equally to this work (remove if not applicable).}
\correspondingauthor{\textsuperscript{1}To whom correspondence should be addressed. E-mail: earn@math.mcmaster.ca}

>>>>

% Please include corresponding author, author contribution and author declaration information
\authorcontributions{{\color{red}
%%Please provide details of author contributions here.
DJDE conceived the project and managed the data entry.  
All authors contributed to design of analyses.
BMB, JD, JM, and DJDE conducted analyses.
DJDE and BMB wrote the paper. 
All authors revised the text and approved the manuscript for submission.
}}
%%\authordeclaration{{\color{red}Please declare any conflict of interest here.}}
%%\equalauthors{\textsuperscript{1}A.O.(Author One) and A.T. (Author Two) contributed equally to this work (remove if not applicable).}
\correspondingauthor{\textsuperscript{1}To whom correspondence should be addressed. E-mail: earn@math.mcmaster.ca}
